```{r}
#| output: false
#| echo: false

# Only edit below this line
#############################################################################
#Postition of Needle Valve O2 IGN
valve_O2_pos <- 9    #Turns from close

#Postition of Neelde valve H2 IGN
valve_H2_pos <- 9  #Turns from close

#Pressure on the O2 pressure reducer
O2_p_red <- 14.9  #in bar

#Pressure on H2 pressure reducer
H2_p_red <- 15.1  #in bar
#############################################################################
# Only edit above this line
```

---
title: "PERSEUS Pre-Detonator Firing "
date: 26.10.2024
author:
  - name: PERSEUS
    email: nbartzsch@ethz.ch
    affiliation: 
      - name: ARIS
        url: https://aris-space.ch/perseus-2024/
editor: visual
format:
  html:
    toc: true
execute:
  warning: false
  eval: true
  echo: false
---

```{r}
#| output: false

##Load libraries

library(tidyverse)
library(gt)
library(readr)
library(here)
```

```{r}
#| output: false
#| echo: false

# Only edit below this line
#############################################################################
# Import data
processed_data_sens <- read_csv(here("data", "processed_data", "processed_data_sens.csv"))

#############################################################################
# Only edit above this line
```

### General Information

The goal of this webpage is to show the data from the Kistler sensors of firings in a more interactive way. The large data sets and very fast phenomena we want to analize are hard to visualize in static graphs.

### Setup Configuration

This section contains all information about the setup of the system. This helps identifying and tracing back the effects of different configurations.

```{r}

#Create df with talbe data
table_geom <- data.frame(
  O2_pos = paste(valve_O2_pos, "[t.f.c]"),
  O2_pre = paste(O2_p_red, "[bar]"),
  H2_pos = paste(valve_H2_pos, "[t.f.c]"),
  H2_pre = paste(H2_p_red, "[bar]")
)

#Create table
table_geom |> 
  gt() |> 
  cols_label(
    O2_pos = ("NV O2 IGN"),
    O2_pre = ("Pressure on O2 PRV"),
    H2_pos = ("NV H2 IGN"),
    H2_pre = ("Pressure on H2 PRV")
  ) |> 
  cols_align(align = "center")
```
