```{r}
#| output: false
#| echo: false

# Only edit below this line
#############################################################################
#Postition of Needle Valve O2 IGN
valve_O2_pos <- 2.5    #Turns from close

#Postition of Neelde valve H2 IGN
valve_H2_pos <- 0.8  #Turns from close

#Pressure on the O2 pressure reducer
O2_p_red <- 6  #in bar

#Pressure on H2 pressure reducer
H2_p_red <- 6  #in bar
#############################################################################
# Only edit above this line
```

---
title: "PERSEUS Pre-Detonator Firing "
date: 26.10.2024
author:
  - name: PERSEUS
    email: nbartzsch@ethz.ch
    affiliation: 
      - name: ARIS
        url: https://aris-space.ch/perseus-2024/
editor: visual
format:
  html:
    toc: true
execute:
  warning: false
  eval: true
  echo: false
---

```{r}
#| output: false

##Load libraries

library(tidyverse)
library(gt)
library(readr)
library(here)
library(plotly)
```

```{r}
#| output: false
#| echo: false

# Only edit below this line
#############################################################################
# Import data
processed_data_sens <- read_csv(here("data", "processed_data", "processed_data_sens.csv"))

#############################################################################
# Only edit above this line
```

### General Information

The goal of this webpage is to show the data from the Kistler sensors of firings in a more interactive way. The large data sets and very fast phenomena we want to analize are hard to visualize in static graphs.

### Setup Configuration

This section contains all information about the setup of the system. This helps identifying and tracing back the effects of different configurations.

```{r}

#Create df with talbe data
table_geom <- data.frame(
  O2_pos = paste(valve_O2_pos, "[t.f.c]"),
  O2_pre = paste(O2_p_red, "[bar]"),
  H2_pos = paste(valve_H2_pos, "[t.f.c]"),
  H2_pre = paste(H2_p_red, "[bar]")
)

#Create table
table_geom |> 
  gt() |> 
  cols_label(
    O2_pos = ("NV O2 IGN"),
    O2_pre = ("Pressure on O2 PRV"),
    H2_pos = ("NV H2 IGN"),
    H2_pre = ("Pressure on H2 PRV")
  ) |> 
  cols_align(align = "center")
```

### Data from Firing

The graph below shows the response from the Kistler sensor in the pre-detonator. The response is given in pC over time in seconds. The plot below is interactive, so the axes can be re scaled and you can zoom in.

The data shown below was sampled at 500kHz.

```{r}
plot_data <-  processed_data_sens |>
  filter(s <= 1.3)|>
  filter(s >= 0.3)

p <- ggplot(plot_data, aes(x = s, y = pC)) +
  geom_path() +
  theme_minimal()+
  labs(x = "Time [s]", y = "Sensor Response [pC]")

interactive_plot <- ggplotly(p)
interactive_plot
```
